The Countercyclical Component of Capital Regulation

### 2020-04-18 Analysis/Draft/Draft_bookdown.Rmd
Finish moments section first draft

According to the theoretical framework presented in section 4.1, an increase in average PD reduces the amount of *Capital savings* if other moments are kept constant. This relationship is illustrated in panel A of Figure \ref{fig:pdmapcases} and empirically tested in Table \ref{tab:moments_contribution}. In all columns of this table average PD is negatively associated with *Capital savings*.

@@

Panel C in table \ref{tab:moments_cyclicality} provides evidence that the observed relationship between PD distribution skewness and the business cycle cannot be explained without portfolion reallocation. All the statistical significant coefficients are positive, contrary to the expectation if banks wouldn't reallocate their portfolio. Considering an economic downturn, the positive coefficients suggest that banks fight the deterioration of their portfolio credit quality by reducing risk taking in new loans. The combination of these two movements, higher PD of existing exposure and lower PD of new assets, results in a less skewed PD distribution during recessions.

Table \ref{tab:moments_contribution} shows that lower skewness translates to higher *Capital savings*. The effect is statistical significant for all except sovereign portfolios. According to column 1, an increase of 0.182 percentage points in PD distribution skewness growth rate (one standard deviation) decreases total *Capital savings* growth rate by 0.009 percentage points on average, representing 20% of total *Capital savings* standard deviation. The effect is even stronger on corporate portfolios accounting for 40% of their *Capital savings* standard deviation.

>>>>

According to the theoretical framework presented in section 4.1, an increase in average PD reduces the amount of *Capital savings* if other moments are kept constant. This relationship is illustrated in panel A of Figure \ref{fig:pdmapcases} and empirically tested in Table \ref{tab:moments_contribution}. In all columns of this table average PD is negatively associated with *Capital savings*. Note that, in Table \ref{tab:moments_contribution}, not only the explained but also explanatory variables change across regressions by portfolio $j$.

@@

Panel C in Table \ref{tab:moments_cyclicality} provides evidence that the observed relationship between PD distribution skewness and the business cycle cannot be explained without portfolion reallocation. All the statistical significant coefficients are positive, contrary to the expectation if banks wouldn't reallocate their portfolio. Considering an economic downturn, the positive coefficients suggest that banks fight the deterioration of their portfolio credit quality by reducing risk taking in new loans. The combination of these two movements, higher PD of existing exposure and lower PD of new assets, results in a less skewed PD distribution during recessions.

Table \ref{tab:moments_contribution} shows that lower skewness translates into higher *Capital savings*. The effect is statistical significant for all except sovereign portfolios. According to column 1, an increase of 0.182 percentage points in PD distribution skewness growth rate (one standard deviation) decreases total *Capital savings* growth rate by 0.009 percentage points on average, representing 20% of total *Capital savings* standard deviation. The effect is even stronger on corporate portfolios accounting for 40% of their *Capital savings* standard deviation. 
The evidence of Panel C in Table \ref{tab:moments_cyclicality} and Table \ref{tab:moments_contribution} suggest that as banks flight to safety in economic recessions, the increase in *Capital savings* due to the associated less skewed PD distribution helps banks to maintain their capital ratios. This countercyclical effect driven by the skewness of the PD distribution is on top of any gain from a lower average PD.
